A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ Using 2013 Plank Cosmology.

### 2014-03-10 paper/draft.tex
Abstract updated

\documentclass[manuscript]{aastex}
%\documentclass[preprint2]{aastex}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

\begin{abstract}
This work relates baryonic matter and dark matter at high redshift using observational data
from the HST and results of the Multidark Simulation.
Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
\end{abstract}

\keywords{LF, SFR, high redshift galaxies, reionization}

@@

In one hand we have observational results: the GLF for star-forming galaxies at high redshift (z=5.9)\citep{bouwens06,willott07}
expressed in terms of magnitude in the ultraviolet range (M1350). In the other hand we have a DMH 
catalog, result from the Multidark Simulation with Plank Cosmology. %\citep{Multidark}

@@

@@

\acknowledgments
Gracias Totales

\appendix

@@

\begin{thebibliography}{}
\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53
\bibitem[Willot(2007)]{willott07} Willott, Chris J. et al. 2013, \aj, 145, 4
\end{thebibliography}

>>>>

\documentclass[manuscript]{aastex}
%\documentclass[preprint2]{aastex}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

\begin{abstract}
This work relates baryonic matter and dark matter at redshift $z=5.9$ using observational data
from CFHTLS\citep{willott13}, HUDF09\citep{bouwens06,bouwens12}, UKIRT and SDXS\citep{mclure09}, and results of the Multidark Simulation \citep{riebe13}
in a cubic box of length $1000 \textrm{Mpc h}^{-1}$. Cosmic variance effects are studied on smaller boxes of length $250 \textrm{Mpc h}^{-1}$.
The luminosity function is fitted in booth sizes. Using the relationship between the UV continuum and Star Formation Rate (SFR) by \cite{kennicutt98}
we get the relationship between the Dark Matter Halos Mass and Star Formation Rate.
%Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
\end{abstract}
\keywords{Dark Matter, LF, SFR, High Redshift Galaxies, Reionization}

@@

In one hand we have observational results: the GLF for star-forming galaxies at high redshift (z=5.9)\citep{bouwens06,willott13}
expressed in terms of magnitude in the ultraviolet range (M1350). In the other hand we have a DMH 
catalog, result from the Multidark Simulation with Plank Cosmology. %\citep{Multidark}

@@

\subsection{The Drop-out Technique - Lyman Break Technique}

@@

\acknowledgments
%Gracias Totales
%
\appendix

@@

\begin{thebibliography}{}
\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53%2006ApJ...653...53B
\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 %2012ApJ...752L...5B
\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 36, 189%1998ARA&A..36..189K
\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196%2009MNRAS.395.2196M
\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 %2013AN....334..691R
\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4%2013AJ....145....4W

\end{thebibliography}
